\textbf{Response Letter}

### 2018-12-24 doc/aij18/major-revision/experiments.tex
update 24 Dec 20.00

  \begin{enumerate}
  \item \textcolor[rgb]{1.00,0.00,0.00}{Other planners such as {\sc FastDownward} were also tested but provided worse experimental results}
  \item \textcolor[rgb]{1.00,0.00,0.00}{A SAT-based planner like {\sc Madagascar} is particularly suitable for tasks where the observed plan trace $\tau$ determines the length of the solution plan (case 1 presented in section \ref{task_definition})}. In this case, the prefix of the solution plan is solvable in two steps (planning horizon length 2) because the actions for inserting preconditions can be applied in parallel in a single step and the same for the actions inserting the effects.
  \item \textcolor[rgb]{1.00,0.00,0.00}{When the length of the plan is unknown (case 2 presented in section \ref{task_definition}), the ability of {\sc Madagascar} to deal with instances populated with dead-ends is very helpful~\cite{lopez2015deterministic}.}
  \end{enumerate}

@@

Figure~\ref{fig:pspace_quality} displays \textcolor{red}{the average precision and recall of the 15 learned models} in the scenario with unknown plan horizon. As expected, the quality of the learned models is lower than when the horizon of the plan is known. \textcolor{red}{The higher complexity of this setting is also reflected in the appearance of some timeouts when solving the learning task. The first timeout is found at $|\mathcal{T}| = 3$ in the \emph{grid} domain, and the number of timeouts increases until it reaches 6 with $|\mathcal{T}| = 10$.} We can observe in Figure~\ref{fig:pspace_quality} the opposite behaviour to Figure~\ref{fig:np_quality}; that is, we find a drop of the quality as the input knowledge increases. The drop in the score is caused by the increasing number of timeouts, meaning that no solution is found in many tasks within the given time-bound, and consequently a value of $0$ for precision and recall is assigned to these experiments. Figure \ref{fig:pspace_time}, on the other hand, reflects that the computation time of the first case study is also higher than in the second case, which is explained by both the higher complexity and the large number of timeouts.

The conclusions we draw from these experiments is that, when the plan horizon is known, learning with few input samples yield action models that contain 95\% of the preconditions and effects of the GTM plus some extra ones as indicated by the values of precision and recall. With unknown plan horizons, on the other hand, the learned models are generally more different from the GTM; while timeouts are the main cause of the drop in the score, we must point out that pure syntax-based metrics are not adequate to evaluate such under-constrained tasks since the phenomenon of \emph{reformulation} occurs and this largely impacts the results (we will provide experimental evidence of this in section \ref{minimal}). \textcolor{red}{These results emphatize a relevant feature our approach, the small size of the training set required by \FAMA in comparison with other approaches (see Table \ref{table:models_comparison2}). Unlike extensive-data approaches, our work explores an alternative research direction to learn action models from small amounts of plan traces. This is an important advantage, particularly in domains in which it is costly or impossible to obtain a significant number of training samples.}

>>>>

  \begin{enumerate}
  \item \textcolor[rgb]{1.00,0.00,0.00}{Other planners such as {\sc FastDownward} were also tested but provided worse experimental results}
  \item \textcolor[rgb]{1.00,0.00,0.00}{A SAT-based planner like {\sc Madagascar} is particularly suitable for tasks where the observed plan trace $\tau$ determines the horizon of the solution plan (case 1 presented in section \ref{task_definition})}. In this case, a SAT-based planner solves the prefix of the solution plan in two time steps because the actions for inserting preconditions can be applied in parallel in a single time step and the same for the actions inserting the effects.
  \item \textcolor[rgb]{1.00,0.00,0.00}{When the length of the plan is unknown (case 2 presented in section \ref{task_definition}), the ability of {\sc Madagascar} to deal with instances populated with dead-ends is very helpful~\cite{lopez2015deterministic}.}
  \end{enumerate}

@@

Figure~\ref{fig:pspace_quality} displays \textcolor{red}{the average precision and recall of the 15 learned models} in the scenario with unknown plan horizon. As expected, the quality of the learned models is lower than when the horizon of the plan is known. \textcolor{red}{The higher complexity of this setting is also reflected in the appearance of some timeouts when solving the learning task. The first timeout is found in the \emph{grid} domain at $|\mathcal{T}| = 3$; the \emph{floortile} times out with $|\mathcal{T}| = 4$; and by the time $|\mathcal{T}|$ reaches 10 the number of domains were no solution is found is 6, adding the \emph{npuzzle, parking, rovers and zenotravel} domains.} We can observe in Figure~\ref{fig:pspace_quality} the opposite behaviour to Figure~\ref{fig:np_quality}; that is, we find a drop of the quality as the input knowledge increases. The drop in the score is caused by the increasing number of timeouts, meaning that no solution is found in many tasks within the given time-bound, and consequently a value of $0$ for precision and recall is assigned to these experiments. Figure \ref{fig:pspace_time}, on the other hand, reflects that the computation time of the first case study is also higher than in the second case, which is explained by both the higher complexity and the large number of timeouts.

The conclusions we draw from these experiments is that, when the plan horizon is known, learning with few input samples yield action models that contain 95\% of the preconditions and effects of the GTM plus some extra ones as indicated by the values of precision and recall. With unknown plan horizons, on the other hand, the learned models are generally more different from the GTM; while timeouts are the main cause of the drop in the score, we must point out that pure syntax-based metrics are not adequate to evaluate such under-constrained tasks since the phenomenon of \emph{reformulation} occurs and this largely impacts the results (we will provide experimental evidence of this in section \ref{minimal}). \textcolor{red}{These results emphasize a relevant feature our approach: the small size of the training set required by \FAMA in comparison with other approaches (see Table \ref{table:models_comparison2}). Unlike extensive-data approaches, our work explores an alternative research direction to learn action models from small amounts of plan traces. This is an important advantage, particularly in domains in which it is costly or impossible to obtain a significant number of training samples.}

### 2018-12-24 doc/aij18/major-revision/learning_action_models.tex
update 24 Dec 20.00

\textcolor[rgb]{1.00,0.00,0.00}{      There will be a validate action in $\pi_\Lambda$ per observed state in $\tau$. The position of the validate actions in $\pi_\Lambda$ will be determined by the planner checking that the state resulting after the execution of an apply action comprises the observed state $s_j\in\tau$.}

@@

The logical inference process our approach is based on has trouble learning preconditions that are not, simultaneously, negative effects as well, since in this case no change can be observed between the pre-state and post-state of an action. This is specially the case for static predicates that never change and, hence, can only be preconditions. In order to address this shortcoming, we apply a post-process based on the one proposed in \cite{kuvcera2018louga}. In their proposal, they obtain a full trace by applying the sequence of actions of the input trace and infer the preconditions from this fully observable trace. In our case, since the sequence of actions of the input trace might not be fully observable, we produce the traces by applying the actions found in the validation part of the solution plan. For instance, in the example of the figure \ref{fig:plan-lplan}, the sequence of actions used to produce the full trace would be {\tt{\small(unstack blockB blockA)}}, {\tt{\small(put-down blockB)}}, {\tt{\small(pick-up blockA)}}, and {\tt{\small(stack blockA blockB)}}. This post-process allows \FAMA to learn more complete lists of preconditions and deal with the always problematic static predicates.

>>>>

\textcolor[rgb]{1.00,0.00,0.00}{There will be a validate action in $\pi_\Lambda$ for every observed state in $\tau$. The position of the validate actions in $\pi_\Lambda$ will be determined by the planner by checking that the state resulting after the execution of an apply action comprises the observed state $s_j\in\tau$.}

@@

The logical inference process our approach is based on has trouble learning preconditions that are not, simultaneously, negative effects as well, since in this case no change can be observed between the pre-state and post-state of an action. This is specially the case for static predicates that never change and, hence, can only be preconditions. In order to address this shortcoming, we apply a post-process based on the one proposed in \cite{kuvcera2018louga}. In their proposal, they obtain a full trace by applying the sequence of actions of the input trace and infering the preconditions from this fully observable trace. In our case, since the sequence of actions of the input trace might not be fully observable, we produce the traces by applying the actions found in the validation part of the solution plan. For instance, in the example of the figure \ref{fig:plan-lplan}, the sequence of actions used to produce the full trace would be {\tt{\small(unstack blockB blockA)}}, {\tt{\small(put-down blockB)}}, {\tt{\small(pick-up blockA)}}, and {\tt{\small(stack blockA blockB)}}. This post-process allows \FAMA to learn more complete lists of preconditions and deal with the always problematic static predicates.
